---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sta545package

<!-- badges: start -->
<!-- badges: end -->

The goal of the sta545package is to implement the methods in David Cox's 1972 paper *Regression Models and Life Tables* for use in a project for the class "STA 545: Statistical Data Mining" at the University of Buffalo.

## Installation

You can install the released version of the sta545package from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("mathmonster/sta545package")
```

## Examples

### Kaplan-Meier Product Limit Estimator:

```{r Kaplan_Meier}
library(sta545package)
plot(fitkm(remission ~ sample, delta="censor", data=leukemia))
```

### Cox Proportional Hazards Model

#### Fit a model

```{r Cox_Model}
fitcox.leukemia <- fitcox(remission ~ sample, delta="censor", data=leukemia)
summary(fitcox.leukemia)
```

#### Making predictions
```{r Cox_Model_Predict}
predict(fitcox.leukemia, newdata=leukemia, type="expected")
```

#### Calculating the c-index
```{r Cox_Model_Concordance}
concordance.fitcox(fitcox.leukemia, newdata=leukemia)
```

#### Cross-validated c-index
```{r Cox_Model_Cross_Validation}
cv.fitcox(leukemia, fitcox(remission ~ sample, delta="censor", data=leukemia), 5)
```
